### 2019-06-07 paper submission 3tex.tex
Add CES utility formula

In our baseline model preferences over sectoral goods aggregate in
Cobb-Douglas fashion. In this robustness check we replace equation (\ref%
{aggregate}) by a CES formulation. This requires calibrating $J$ \
\textquotedblleft share\textquotedblright\ parameters, as well as an
elasticity of substitution. Our strategy is to calibrate the share
parameters by matching the share of each final good sector in global expenditure for each year. 
We then look at how our results vary with different
values of the elasticity of substitution.

>>>>

In our baseline model preferences over sectoral goods aggregate in
Cobb--Douglas fashion. In this robustness check we replace equation (\ref%
{aggregate}) by a CES formulation, 
\begin{equation}
C_{nt} = \left[
	\sum_{j=1}^{J}
		\left( \nu_{t}^{j}\right) ^{1/\sigma}
		\left( C_{nt}^{j}\right) ^{(\sigma-1)/\sigma}
	\right]^{\sigma/(\sigma-1)},
\label{ces_aggregate}
\end{equation}%
where $\sigma>0$ is the elasticity of substitution across sectors and $\nu_{t}^j$ is a demand shifter. We normalize $\sum_{j=1}^J \nu_t^j=1$. As in the Cobb--Douglas case, we let demand shifters vary over time.

This requires calibrating the $J$ demand parameters $\nu_{t}^j$ for each year, as well as the
elasticity of substitution $\sigma$. Our strategy is to calibrate the demand
parameters by matching the share of each final good sector in global expenditure for each year. 
We then look at how our results vary with different
values of the elasticity of substitution.
